Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-10-07 Manuscript/manuscript.tex
Written a short description of the choice of scaling factor 0.75 for PS compared to 0.8 for PC.in the methods section.
The other rubbish is still left there.

>>>>

The polarization of electrons in ECC-lipids uses the implicit method termed electronic continuum correction (ECC). \cite{leontyev09, Pluharova2014, martinek17, melcr18} 
In this method, the effects of electronic polarization are represented through rescaling of charges. \cite{melcr18}
The scaling factor is derived from the high-frequency dielectric constant of electrons, $\epsilon_{el}$, as
\begin{equation}
f_q = \frac{1}{\sqrt{\epsilon_{el}}} .
\end{equation}
The value of $\epsilon_{el}$ for water solutions is $\epsilon_{el} = 1.78$ \cite{leontyev09},
hence, the scaling factor yields $f_q \approx 0.75$.

In the case of POPS, which is a monovalently negatively charged lipid, 
we used exactly this scaling factor to represent the polarizability of the electrons
yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}

Note that we used a different scaling factor of $f_q = 0.8$ 
to derive a ECC-POPC model, which also uses ECC. \cite{melcr18}
Compared to POPS, POPC is a zwitterionic neutral molecule with a zero total charge; 
scaling it by any factor does not affect it. 
Partial charges of the atoms in POPC are not physical observabels, 
and vary greatly between different models. \cite{botan15, catte16, nmrlipids_proj4, Pluhackova2016}
The choice of a larger scaling factor in ECC-POPC represents the fact that 
the set of partial charges in the initial model for ECC-POPC, the Lipid14 model \cite{dickson14}, 
was determined as less polar compared to other models.

\textbf{This explains the choice of different scaling factor. uff..}
